---
title: "s3oop-Joe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{s3oop-Joe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(s3oopJoe)
```

# Introduction

`s3oopJoe` is a package used to test for Null Hypothesis using the function ttest

# Functions

There are three function is used in this package.
1. Constructor
2. Print method
3. Plot method


# Constructor

The first function is `myttest` which takes in two parameters.
The first sample population (x) and second sample population (y),
Alpha values and a logical parameter stating if the mean populations are paired
it outputs a list of useful information based on the function which are further
processed by the methods functions.
This list is stored in a class which is called Rttest

```{r}
x <- rnorm(30, 20, 10)
y <- rnorm(30, 10, 12)
ans <- myttest(x=x, y=x, alpha=0.05, paired = FALSE)


```
# Method1
The first method is the plot function
which makes a box plot of the two samples "x" and "y"
```


This is called using the class Rttest
```{r}

plot(ans)

```



# Method2
The second method is the print function
print.Rttest() which prints the confidence Interval

```


This is called using the
```{r}
print(ans)
```

# Shiny App

This is used to package the function in an App 

```{r,eval = FALSE}
plotShiny()



